---
title: "VIF"
author: "Group_ISSP"
date: "12/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing Libraries

```{r} 
library(readxl)
library(dplyr)
library(fmsb)
```


```{r}
data <- read.csv('new_scaled.csv')
df = data[,-c(1,24,25)]
```

```{r}
vif_func<-function(in_frame,thresh=10,trace=T,...)
  {
  require(fmsb)
  
  if(class(in_frame) != 'data.frame') in_frame<-data.frame(in_frame)
  
  #get initial vif value for all comparisons of variables
  vif_init<-NULL
  var_names <- names(in_frame)
  for(val in var_names)
    {
    regressors <- var_names[-which(var_names == val)]
    form <- paste(regressors, collapse = '+')
    form_in <- formula(paste(val, '~', form))
    vif_init<-rbind(vif_init, c(val, VIF(lm(form_in, data = in_frame, ...))))
    }
  vif_max<-max(as.numeric(vif_init[,2]), na.rm = TRUE)
  
  if(vif_max < thresh)
    {
    if(trace==T)
      { #print output of each iteration
      prmatrix(vif_init,collab=c('var','vif'),rowlab=rep('',nrow(vif_init)),quote=F)
      cat('\n')
      cat(paste('All variables have VIF < ', thresh,', max VIF ',round(vif_max,2), sep=''),'\n\n')
      }
    return(var_names)
    }
  
  else
    {
    
    in_dat<-in_frame
    
    #backwards selection of explanatory variables, stops when all VIF values are below 'thresh'
    while(vif_max >= thresh)
      {
      
      vif_vals<-NULL
      var_names <- names(in_dat)
      
      for(val in var_names)
        {
        regressors <- var_names[-which(var_names == val)]
        form <- paste(regressors, collapse = '+')
        form_in <- formula(paste(val, '~', form))
        vif_add<-VIF(lm(form_in, data = in_dat, ...))
        vif_vals<-rbind(vif_vals,c(val,vif_add))
        }
      max_row<-which(vif_vals[,2] == max(as.numeric(vif_vals[,2]), na.rm = TRUE))[1]
      
      vif_max<-as.numeric(vif_vals[max_row,2])
      
      if(vif_max<thresh) break
      
      if(trace==T){ #print output of each iteration
        prmatrix(vif_vals,collab=c('var','vif'),rowlab=rep('',nrow(vif_vals)),quote=F)
        cat('\n')
        cat('removed: ',vif_vals[max_row,1],vif_max,'\n\n')
        flush.console()
        }
      
      in_dat<-in_dat[,!names(in_dat) %in% vif_vals[max_row,1]]
      }
    
    return(names(in_dat))
    }
  }
```

```{r}
vif<- vif_func(in_frame=df,thresh=5,trace=T)
vif
```

## The output of VIF with variables without multicollinearity:
'''
var                                   vif             
 Days.since.account.creation           1.04019377991278
 Covid.Policy.Changes.hospital.changes 1.7611849229838 
 Covid.specific.event                  1.82041175410335
 Event                                 1.37656857595958
 General.covid.awareness               1.44977905321228
 Health.Education.Awareness            1.77223940915485
 Hospital.Promotion                    5.21697421323313
 Hospital.specific.covid.education     1.89528453429816
 Job.Posting.Hiring                    1.82531387154575
 Miscellaneous                         1.85152600066952
 No.Image.Video                        1.05484020312986
 Urban                                 1.10722535302754
 EVENING                               1.09321379565343
 MORNING                               1.01678374566184
 NIGHT                                 1.10941013118167
 Weekend                               1.026041812792  
 Likes                                 1.12271317446215
'''